The Globular Cluster System of the Auriga Simulations

### 2019-01-02 Partial/FeH_logM.tex
Mass-weighted Rgc binning v1.0 done

\begin{figure*}[h!]
    \includegraphics[width=\textwidth]{{logMFeH}.png}
    \caption{
        This figure summarises above findings. TODO: write caption for 
        paper.
        \label{fig:todo6}
    }
\end{figure*}

\section{Distribution of Galactocentric radii R$_{\rm GC}$}
\label{sec:Rgc}

>>>>

\begin{figure*}[h!]
    \includegraphics[width=\textwidth]{{logMFeH}.png}
    \caption{
        This figure summarises above findings. TODO: write caption for 
        paper.
        \label{fig:todo6}
    }

    \includegraphics[width=0.32\textwidth]{{logMFeH_Au6}.png}
    \includegraphics[width=0.32\textwidth]{{logMFeH_Au16}.png}
    \includegraphics[width=0.32\textwidth]{{logMFeH_Au24}.png}
    \caption{Same figure, but now colours indicate resolution: L3 green, L4 
        orange, and L5 blue. \emph{Left:} Auriga halo 6. \emph{Mid:} Auriga halo
        16. \emph{Right:} Auriga halo 24. For all three haloes we find marginal
        increases in the mass normalization with increasing resolution level.
        \label{fig:logMFeH_res}
    }
\end{figure*}
\clearpage

\afterpage{%
\section{Distribution of Galactocentric radii R$_{\rm GC}$}
\label{sec:Rgc}
\thispagestyle{empty}
\begin{figure*}[h!]
    \includegraphics[width=0.49\textwidth]{{logMRgc_OldStars_plot-all-trim}.png}
    \includegraphics[width=0.49\textwidth]{{logMRgc_OldStars_plot-errorbar-trim}.png}
    \caption{
        \emph{Left:} Mass-weighted R$_{\rm GC}$ distribution of 
        all Auriga haloes (level 3, 4 and 5).
        \emph{Right:} 
        \label{fig:todo7}
    }

    \includegraphics[width=0.49\textwidth]
        {{logMRgc_OldAccreted_plot-hist2d-with-mean}.png}
    \includegraphics[width=0.49\textwidth]
        {{logMRgc_OldInsitu_plot-hist2d-with-mean}.png}
    \caption{
        \emph{Left:} 
        \emph{Right:}
        \label{fig:todo8}
    }
\end{figure*}
\clearpage
}
\clearpage
\begin{figure*}[h!]
    \includegraphics[width=\textwidth]{{logMRgc}.png}
    \caption{
        This figure summarises above findings. TODO: write caption for 
        paper.
        \label{fig:todo6}
    }

    \includegraphics[width=0.32\textwidth]{{logMRgc_Au6}.png}
    \includegraphics[width=0.32\textwidth]{{logMRgc_Au16}.png}
    \includegraphics[width=0.32\textwidth]{{logMRgc_Au24}.png}
    \caption{Same figure, but now colours indicate resolution: L3 green, L4 
        orange, and L5 blue. \emph{Left:} Auriga halo 6. \emph{Mid:} Auriga halo
        16. \emph{Right:} Auriga halo 24. For all three haloes we find marginal
        increases in the mass normalization with increasing resolution level.
        \label{fig:logMFeH_res}
    }
\end{figure*}
\clearpage
